\Huge Conferences in an Era of Expensive Carbon

### 2019-06-17 main.tex
More

However, going beyond these simple steps is going to be much more
challenging.  One reason is that it isn't actually very clear what changes
will help significantly.  (Describe some of our data.)  More data and
thorough analysis is needed.

Another reason why going beyond simple measures is hard is that, although
conferences damage the climate, they also create significant value.  Science
is a fundamentally social process, and the conference system accelerates
research through high-bandwidth interaction, direct dissemination of
results, network building, and serendipitous cross-fertilization.

@@

Fortunately, there is a well-established mechanism for comparing apples and
oranges---indeed, for comparing almost anything!  Economists call it ``the
magic of markets.''  By mapping choices and preferences in disparate domains
onto a common scale (i.e., money), economic markets function as massively
distributed computations that optimize costs and benefits across vastly
different activities.\bcp{Give a simple, concrete example.}  For this
reason, many policy experts advocate addressing climate change through some
form of carbon pricing, which places a monetary cost on greenhouse gas
emissions, sending a clear market signal that changes aggregate
behavior.\bcp{See
  https://kleinmanenergy.upenn.edu/policy-digests/why-carbon-pricing-falls-short
  for lots of good phrasing and citations.}

>>>>

However, going beyond these simple steps is going to be much more
challenging.  One reason is that it isn't actually very clear what changes
will help significantly.  (Describe some of our data.  Show the two
diagrams.  Draw some conclusions / discuss why it's hard to draw
conclusions.)  More data and more thorough analysis is needed.

But there is another, deep reason why going beyond simple measures is hard:
while conferences damage the climate, they also create significant value!
Science is a fundamentally social process, and the conference system
accelerates research through high-bandwidth interaction, direct
dissemination of results, network building, and serendipitous
cross-fertilization.

@@

Fortunately, we have a well-established mechanism for comparing apples and
oranges---indeed, for comparing almost anything!  Economists call it ``the
magic of markets.''  By mapping choices and preferences in disparate domains
onto a common scale (i.e., money), economic markets function as massively
distributed computations that optimize costs and benefits across vastly
different activities.\bcp{Give a simple, concrete example.}  For this
reason, many policy experts advocate addressing climate change through some
form of carbon pricing, which places a monetary cost on greenhouse gas
emissions, sending a clear market signal that changes aggregate
behavior.\bcp{See
  https://kleinmanenergy.upenn.edu/policy-digests/why-carbon-pricing-falls-short
  for lots of good phrasing and citations.}
